The \dealii Library, Version 9.1

### 2019-06-05 9.1/paper.tex
Add Graham Harper to name and affiliation list

\hypersetup{
  pdfauthor={
    Daniel Arndt,
    Wolfgang Bangerth,
    Denis Davydov,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler,
    Ross Maguire Kynch,
    Matthias Maier,
    Jean-Paul Pelteret,
    Bruno Turcksin,
    David Wells
  },
  pdftitle={The deal.II Library, Version 9.1, 2019},
}

@@

\author[2]{Wolfgang~Bangerth}
\affil[2]{Department of Mathematics, Colorado State University, Fort
  Collins, CO 80523-1874, USA.
  {\texttt{bangerth@colostate.edu}}}

@@

>>>>

\hypersetup{
  pdfauthor={
    Daniel Arndt,
    Wolfgang Bangerth,
    Denis Davydov,
    Graham Harper
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler,
    Ross Maguire Kynch,
    Matthias Maier,
    Jean-Paul Pelteret,
    Bruno Turcksin,
    David Wells
  },
  pdftitle={The deal.II Library, Version 9.1, 2019},
}

@@

\author[2]{Wolfgang~Bangerth}
\affil[2]{Department of Mathematics, Colorado State University, Fort
  Collins, CO 80523-1874, USA.
  {\texttt{bangerth@colostate.edu}, 
   \texttt{harper@math.colostate.edu}}}

@@

\author[2]{Graham Harper}
